Concurrent Programming with Harmony

### 2020-07-30 book/paper.tex
Added an exercise

\section*{Exercises}
\begin{problems}
\item Assume that you have only binary semaphores.
Implement counting semaphores using split binary semaphores.
\item With reader/writer locks,
it can be useful for a process to \emph{downgrade} its write lock
to a read lock when its done writing but not done reading.  Implement
a \texttt{downgrade} method.  Note, you cannot do this simply by releasing the
write lock and then obtaining the read lock, because the process needs
to remain in the critical section.
\item Implement a solution to the producer/consumer problem
(\autoref{fig:boundedbuffer}) using split binary semaphores.
\item \label{ex:onelane} Cornell's campus features some one-lane bridges.
Cars can only go in one direction at a time. Consider northbound
and southbound cars wanting to cross a one-lane bridge.
The bridge allows arbitrary many cars, as long as they're going in the
same direction.
Implement a lock that observes this requirement using SBS.  Write methods
\texttt{nb\_enter()} that a car must invoke before going northbound on
the bridge and \texttt{nb\_leave()} that the car must invoke after leaving
the bridge.  Similarly write \texttt{sb\_enter()} and \texttt{sb\_leave()}
for southbound cars.

>>>>

\section*{Exercises}
\begin{problems}
\item Assume that you have only binary semaphores.
Implement counting semaphores using the split binary semaphores technique.
\item With reader/writer locks,
it can be useful for a process to \emph{downgrade} its write lock
to a read lock when its done writing but not done reading.  Add
a \texttt{downgrade} method to the code in \autoref{fig:RWsplitsema}.
How easy or hard would it be to do the same for the code in
\autoref{fig:rw2lock}?
Note, you cannot simply release the
write lock and then obtain the read lock, because the process needs
to remain in the critical section.
\item \label{ex:onelane} Implement a solution to the producer/consumer problem
(\autoref{fig:boundedbuffer}) using split binary semaphores.
\item \label{ex:onelane} Cornell's campus features some one-lane bridges.
On a one-lane bridge,
cars can only go in one direction at a time. Consider northbound
and southbound cars wanting to cross a one-lane bridge.
The bridge allows arbitrary many cars, as long as they're going in the
same direction.
Implement a lock that observes this requirement using SBS.  Write methods
\texttt{nb\_enter()} that a car must invoke before going northbound on
the bridge and \texttt{nb\_leave()} that the car must invoke after leaving
the bridge.  Similarly write \texttt{sb\_enter()} and \texttt{sb\_leave()}
for southbound cars.
\item Extend the solution to \autoref{ex:onelane} by implementing the
requirement that at most 3 cars are allowed on the bridge.
